Setup Honeypot: Team Contagiarium

### 2011-11-01 Setup_honeypot.tex
Subsection DenyHosts toegevoegd. Misschien nog wat uitbereiding nodig?

>>>>

\subsection{DenyHosts}
If someone finds out our real SSH port changed to 9022, they might try to break into this port. To make sure no bruteforce attacks can be done on this port, DenyHosts is installed. This program blocks IP-adresses that try to log in more than 3 times, with the wrong password. The blocked hosts are blacklisted on the honeypot, so we can edit them if needed.
